---
title: "FTF Initiative Performance Scorecard FY 2023"
output: 
  word_document: 
    reference_doc: "~/R_scripts/country_scorecards/country_scorecards/templates/v1scorecard_template.docx"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warnings = FALSE)
library(usaidplot)
# library(cowplot)
library(patchwork)
library(ggplot2)
library(ggrepel)
library(tidyverse)
library(readxl)
library(extrafont)
library(extrafontdb)
library(DBI)
library(RSQLite)
library(disR)
library(googlesheets4)
gs4_auth(email = "rythomas@usaid.gov")
source("../R/03_load_data.R")
source("../R/05_helpers.R")
source("../R/02_make_scorecard_plots.R")
ou_name  <- "FTF Initiative"

n_activities <- active_activities_unique %>%  nrow()
dna_udns <- c("3.5.1.2.4", "3.6.1.2.4", "3.7.1.2.4", "3.5.2.2.4", "3.6.2.2.4", "3.7.2.2.4")
other_udns <- c("3.5.1.2.3", "3.6.1.2.3", "3.7.1.2.3", "3.5.2.2.3", "3.6.2.2.3", "3.7.2.2.3")
finance_sex_dna <- extract %>%
  filter(year == 2023 & ic=="EG.3.2-27" & udn %in% dna_udns) %>%
  summarize(dna = sum_(actual))
finance_sex_mixed <- extract %>%
  filter(ro == ro & ou == ou_name & year == 2023 & ic=="EG.3.2-27" & udn %in% other_udns) %>%
  summarize(mixed = sum_(actual))
total_financing <- extract %>%
  filter(year == 2023 & ic=="EG.3.2-27" & udn == "3") %>%
  summarise(total = sum_(actual)) %>% "["("total")
ou_dat <- pt_dat %>% filter(ou == ou_name) %>% arrange(ro, ou, year, type, name)

scores <- data.frame(
    pt = c("PT1", "PT2", "PT3", "PT4", "PT5")
    , name = c("sales", "financing", "hectares", "psi", "mddw")
    , y = rep(1,5)
    , score = factor(rep("Not applicable", 5)
                     , levels = c("On track", "Not on track", "Not applicable", "Not available"))
  )
section1 <- s1_plot(dat = input_dat
                    , active_activities_dat = active_activities_dat
                    , ou_name = ou_name
                    , mddw = mddw_dat
                    , ou_dat = ou_dat
                    , n_activities = n_activities
                    , finance_sex_dna = finance_sex_dna
                    , total_financing = total_financing
                    , finance_sex_mixed = finance_sex_mixed
                    , scores = scores)
```

This Feed the Future (FTF) Performance Scorecard assesses the `r paste0(trimws(gsub("\\(.*$", "", ou_name )))` progress toward FY 2030 Performance Targets.

# Performance Overview

```{r stars, fig.width=6.5, fig.height=.75, warning=FALSE, message=FALSE}
section1["stars_plot"]$stars_plot + section1["overall_score_text"]$overall_score_text +
  plot_layout( ncol = 2, widths = unit(c(2, 4.5), c("in")))
```

The FY 2023 **On track** value is determined by drawing a line from the baseline (FY 2022) to the FY 2030 Target. For FY 2023, Performance Targets are considered **On track** if they have reported at least 90% of that value.

```{r overview plot, warning=FALSE, message=FALSE, fig.width = 6.5, fig.height=2.75}
summary_dat <- pt_upload %>%
  pivot_longer(c(actual_norm, interim_target_norm)
               , names_to = "type"
               , values_to = "value") %>%
  mutate(type = case_when(type == "actual_norm" ~ "FY23 Actual"
                          , type == "interim_target_norm" ~ "90% of FY23 'On track' Target")
         , name = case_when(name == "PT3: Climate hectares" ~ "PT3: Climate adaptive hectares", .default = name)) %>% 
  filter(ou == ou_name) %>%
  mutate(name = fct_rev(name), ou_track = case_when(type == "FY23 Actual"~ ou_track)) 

summary_plot <- summary_dat %>%
  mutate(value = case_when(type == "90% of FY23 'On track' Target" ~ value *0.9, .default = value)
         # , value = case_when(value > 1 ~ 1.01, .default = value)
         # , ou_track = case_when(value == 1.01 ~ "On track*", .default = ou_track)
         ) %>% 
  ggplot(aes(y = name, x=value*100, color = fct_rev(type), label = ou_track)) +
  geom_line(aes(group=name), color = "#8C8985", size = 1, show.legend = FALSE) +
  geom_point(stat = "identity", size = 2.3) + 
  # scale_color_manual(values = list("FY23 Interim Target" = "#c9c9c9", "FY23 Actual" = "#8C8985")) +
  # new_scale_color() +
  geom_vline(xintercept = 100, colour = "#0067B9") +
  geom_text_repel(x = 2, nudge_y = .05
            , color = ifelse(summary_dat$ou_track == "On track", "#00B050"
                    #, ifelse(dat$ou_track == "On track*", "#00B050"
                    , ifelse(summary_dat$ou_track == "Not on track", "#f4231a", "#c9c9c9"))
            , show.legend = F, family = "Gill Sans MT"
            , hjust = 0, fontface = "bold") +
  # geom_text(aes(x = 100, y = 4.5, label = "FY30 Performance Target")
  #           , colour = "#0067B9", show.legend = FALSE) +

  usaid_plot() + common_theme() + 
  scale_color_manual(values = c("90% of FY23 'On track' Target" = "#BA0C2F", "FY23 Actual" = "#002F6C")
                     , breaks = c("FY23 Actual", "90% of FY23 'On track' Target")) +
  xlab("Percentage of FY 2023 'On track' Target") + ylab("") +
  theme(legend.position = "bottom"
        , panel.grid.major.y = ggplot2::element_blank()
        , panel.grid.minor.x = ggplot2::element_line(color = "#CFCDC9")) +
  xlim(c(0, NA)) + #ylim(c(NA, 6)) +
  labs(title = "FTF Performance Targets Snapshot"
       # , caption = "*FY23 annual value exceeds the FY30 Performance Target"
       )
summary_plot
```

**Note:** *For Performance Target 2 (Gender financing ratio), the target is to increase financing to females for those OUs that are already achieving parity (\$1).*

*For Performance Target 4 (PSI), all targets are relative to the last three years’ reporting. In future years, the interim targets may increase.*

*For Performance Target 5 (MDD-W), all FY23 actual values are also the baseline, and may have been collected in a prior year. See the detail page for more information.*

*See detailed [methodology document](https://docs.google.com/document/d/13n-43ppFiGKauscQ7HaAiQDCM4DssGEgRdq2fMyTDn0/edit) here. If you have questions, please email the FTF Data and Analytics team at* [refs.adl.da\@usaid.gov](mailto:refs.adl.da@usaid.gov){.email}.

### Performance Target (PT) Details

This section shows PT scores for each applicable PT for `r paste0(trimws(gsub("\\(.*$", "", ou_name )))`.

## Performance Target 1: Value of annual sales of producers and firms receiving USG assistance

```{r sales text, fig.width=6.5, fig.height=.5, warning=FALSE, message=FALSE}
section1["sales_text"]$sales_text
#scales::dollar_format()(this_year$value)
```

```{r sales plot, fig.width=6.5, fig.height=4, warning=FALSE, message=FALSE}
section1["sales_plot"]$sales_plot
```

`r paste(section1["sales_txt"]$sales_txt)`

###### Performance Target 2: Value of financing accessed by female FTF participants per \$1 of financing accessed by male FTF participants

```{r gender text,  fig.width=6.5, fig.height=.5, warning=FALSE, message=FALSE}
# finance
section1["gf_text"]$gf_text
```

```{r gender plot, fig.width=6.5, fig.height=4, warning=FALSE, message=FALSE}
section1["gender_finance_plot"]$gender_finance_plot
```

`r section1["gf_txt"]$gf_txt`

###### Performance Target 3: Number of cultivated hectares under climate adaptation/climate risk management practices and technologies with USG assistance

```{r hectares text, fig.width=6.5, fig.height=.5, warning=FALSE, message=FALSE}
section1["ht_text"]$ht_text
```

```{r hectares plot, fig.width=6.5, fig.height=4, warning=FALSE, message=FALSE}
section1["hectares_plot"]$hectares_plot
```

`r section1["ht_txt"]$ht_txt`

###### Performance Target 4: Value of private sector investment leveraged by the USG to support food security and nutrition

```{r PSI text, fig.width=6.5, fig.height=.5, warning=FALSE, message=FALSE}
section1["psi_text"]$psi_text
```

```{r PSI details, fig.width=7.5, fig.height=4.5, warning=FALSE, message=FALSE}
section1["psi_plot"]$psi_plot
```

`r section1["psi_txt"]$psi_txt`

###### Performance Target 5: Percent of women consuming a diet of minimum diversity (MDD-W)

```{r mddw details, fig.width=6.5, fig.height=.75, warning=FALSE, message=FALSE}
section1["mddw_text"]$mddw_text
```

```{r mddw plot, fig.width=6.5, fig.height=4, warning=FALSE, message=FALSE}
section1["mddw_plot"]$mddw_plot
```

`r section1["mddw_txt"]$mddw_txt`


## Budget Trend

At the Operating Unit level, the Performance Targets are based in part on the FY 2024 budget request. The budget chart below includes EG.3 money only.

```{r budget plot, fig.width=6.5, fig.height=4, warning=FALSE, message=FALSE}
# Budget --------
# ou_budget <- budget %>% filter(year %in% 2020:2024 & ou == trimws(gsub("\\(.*$", "", gsub("USAID ", "",  ou_name )))) %>%
#   mutate(budget = ifelse(ou == "Bureau for Resilience and Food Security (RFS)", budget/2, budget)
#          , type = ifelse(year > 2024, "653(a) Actual", "Requested")) 
# budget_hline <- ou_budget %>% filter(year == 2023) %>%
#   select(budget) %>% as.numeric()
# # # ----------- Prep data
# budget_plot <- ou_budget  %>%
#   rename(`Fiscal Year` = year, `EG3 Budget (000)` = budget) %>%
#   # ------------ ggplot
#   ggplot(aes(x = `Fiscal Year`, y = `EG3 Budget (000)`, linetype = type)) +
#   geom_point(size = 2.3) + geom_line(linewidth = 1, linetype = 4) +
#   geom_label_repel(aes(label = scales::dollar_format()(`EG3 Budget (000)`)), nudge_y = 100) +
# 
#   geom_hline(color = "#BA0C2F", yintercept = budget_hline, linewidth = 1, linetype = 2) +
#   # ------------ Set themes
#   # guides(color = guide_legend(position = "inside")) +
#   usaid_plot() + #common_theme() + 
#   theme(legend.position="bottom", plot.caption = element_text(size = 12) ) +
#   scale_y_continuous(labels = scales::label_dollar(), limits = c(0, NA)) +
#   ylab("") + xlab("") + 
#   # ggtitle(label = "EG3 Budget", subtitle = "Horizontal line is baseline") +
#   # labs(caption = "*REFS' targets were based on *half* of the FY 2023 budget request.")
#   labs(caption = paste0("* Values are in $1,000s\n**Red dashed line is the budget level used for target setting.", collapse="n"))
# budget_plot

make_ftf_budget_plot(ftf_budget, ou_name = ou_name)
```


