---
title: "`r paste0('FTF FY 2023 Performance Scorecard ',paste0(trimws(gsub('USAID ','',gsub('\\(.*$','',params$ou_name )))) )`"
output: 
  word_document: 
    reference_doc: "~/R_scripts/country_scorecards/country_scorecards/v1scorecard_template.docx"
params:
  ou_name: ou_name
  input_dat: input_dat
  extract: extract
  pt_dat: pt_dat
  pt_upload: pt_upload
  active_activities_dat: active_activities_dat
  active_activities_unique: active_activities_unique
  kin: kin
  mddw_dat: mddw_dat
  scores: scores
  national_df: national_df
  ati: ati
  top5_disbursements: top5_disbursements
  top5_results: top5_results
  budget: budget
  ftf_budget: ftf_budget
  mapfile: mapfile
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warnings = FALSE)
library(usaidplot)
# library(cowplot)
library(patchwork)
library(ggplot2)
library(ggrepel)
library(tidyverse)
library(readxl)
library(extrafont)
library(extrafontdb)
library(DBI)
library(RSQLite)
library(disR)
source("10_helpers.R")
source("02_make_scorecard_plots.R")

n_activities <- params$active_activities_unique %>% filter(ro == ro, ou == ou_name) %>%
      distinct(a_code) %>% arrange(a_code) %>% nrow()
dna_udns <- c("3.5.1.2.4", "3.6.1.2.4", "3.7.1.2.4", "3.5.2.2.4", "3.6.2.2.4", "3.7.2.2.4")
other_udns <- c("3.5.1.2.3", "3.6.1.2.3", "3.7.1.2.3", "3.5.2.2.3", "3.6.2.2.3", "3.7.2.2.3")
finance_sex_dna <- params$extract %>%
  filter(ro == ro & ou == ou_name & year == 2023 & ic=="EG.3.2-27" & udn %in% dna_udns) %>%
  summarize(dna = sum_(actual))
finance_sex_mixed <- params$extract %>%
  filter(ro == ro & ou == ou_name & year == 2023 & ic=="EG.3.2-27" & udn %in% other_udns) %>%
  summarize(mixed = sum_(actual))
total_financing <- params$extract %>%
  filter(ro == ro & ou == ou_name & year == 2023 & ic=="EG.3.2-27" & udn == "3") %>%
  summarise(total = sum_(actual)) %>% "["("total")
ou_dat <- params$pt_dat %>% filter(ou == ou_name) %>% arrange(ro, ou, year, type, name)

section1 <- s1_plot(dat = params$input_dat
                    , ou_name = params$ou_name
                    , mddw = params$mddw_dat
                    , ou_dat = ou_dat
                    , n_activities = n_activities
                    , finance_sex_dna = finance_sex_dna
                    , total_financing = total_financing
                    , finance_sex_mixed = finance_sex_mixed
                    , scores = params$scores)
```

This Feed the Future (FTF) Performance Scorecard assesses the `r paste0(trimws(gsub("\\(.*$", "", params$ou_name )))` progress toward FY 2030 Performance Targets.

# Performance Overview

```{r stars, fig.width=6.5, fig.height=.75, warning=FALSE, message=FALSE}
section1["stars_plot"]$stars_plot + section1["overall_score_text"]$overall_score_text +
  plot_layout( ncol = 2, widths = unit(c(2, 4.5), c("in")))
```

The FY 2023 **On track** value is determined by drawing a line from the baseline (FY 2022) to the FY 2030 Target. For FY 2023, Performance Targets are considered **On track** if they have reported at least 90% of that value.

```{r overview plot, warning=FALSE, message=FALSE, fig.width = 6.5, fig.height=2.75}
summary_dat <- params$pt_upload %>%
  pivot_longer(c(actual_norm, interim_target_norm)
               , names_to = "type"
               , values_to = "value") %>%
  mutate(type = case_when(type == "actual_norm" ~ "FY23 Actual"
                          , type == "interim_target_norm" ~ "90% of FY23 'On track' Target")
         , name = case_when(name == "PT3: Climate hectares" ~ "PT3: Climate adaptive hectares", .default = name)) %>% 
  filter(ou == ou_name) %>%
  mutate(name = fct_rev(name), ou_track = case_when(type == "FY23 Actual"~ ou_track)) %>% 
  filter(name != "PT4: Private sector investment")

summary_plot <- summary_dat %>%
  mutate(value = case_when(type == "90% of FY23 'On track' Target" ~ value *0.9, .default = value)
         # , value = case_when(value > 1 ~ 1.01, .default = value)
         # , ou_track = case_when(value == 1.01 ~ "On track*", .default = ou_track)
         ) %>% 
  ggplot(aes(y = name, x=value*100, color = fct_rev(type), label = ou_track)) +
  geom_line(aes(group=name), color = "#8C8985", size = 1, show.legend = FALSE) +
  geom_point(stat = "identity", size = 2.3) + 
  # scale_color_manual(values = list("FY23 Interim Target" = "#c9c9c9", "FY23 Actual" = "#8C8985")) +
  # new_scale_color() +
  geom_vline(xintercept = 100, colour = "#0067B9") +
  geom_text_repel(x = 2, nudge_y = .05
            , color = ifelse(summary_dat$ou_track == "On track", "#00B050"
                    #, ifelse(dat$ou_track == "On track*", "#00B050"
                    , ifelse(summary_dat$ou_track == "Not on track", "#f4231a", "#c9c9c9"))
            , show.legend = F, family = "Gill Sans MT"
            , hjust = 0, fontface = "bold") +
  # geom_text(aes(x = 100, y = 4.5, label = "FY30 Performance Target")
  #           , colour = "#0067B9", show.legend = FALSE) +

  usaid_plot() + common_theme() + 
  scale_color_manual(values = c("90% of FY23 'On track' Target" = "#BA0C2F", "FY23 Actual" = "#002F6C")
                     , breaks = c("FY23 Actual", "90% of FY23 'On track' Target")) +
  xlab("Percentage of FY 2023 'On track' Target") + ylab("") +
  theme(legend.position = "bottom"
        , panel.grid.major.y = ggplot2::element_blank()
        , panel.grid.minor.x = ggplot2::element_line(color = "#CFCDC9")) +
  xlim(c(0, NA)) + #ylim(c(NA, 6)) +
  labs(title = "FTF Performance Targets Snapshot"
       # , caption = "*FY23 annual value exceeds the FY30 Performance Target"
       )
summary_plot
```

**Note:** *For Performance Target 2 (Gender financing ratio), the target is to increase financing to females for those OUs that are already achieving parity (\$1).*

*For Performance Target 4 (PSI), all targets are relative to the last three years’ reporting. In future years, the interim targets may increase.*

*For Performance Target 5 (MDD-W), all FY23 actual values are also the baseline, and may have been collected in a prior year. See the detail page for more information.*

*See detailed [methodology document](https://docs.google.com/document/d/13n-43ppFiGKauscQ7HaAiQDCM4DssGEgRdq2fMyTDn0/edit) here. If you have questions, please email the FTF Data and Analytics team at* [refs.adl.da\@usaid.gov](mailto:refs.adl.da@usaid.gov){.email}.

### Performance Target (PT) Details

This section shows PT scores for each applicable PT for `r paste0(trimws(gsub("\\(.*$", "", params$ou_name )))`.

## Performance Target 1: Value of annual sales of producers and firms receiving USG assistance

```{r sales text, fig.width=6.5, fig.height=.5, warning=FALSE, message=FALSE}
section1["sales_text"]$sales_text
#scales::dollar_format()(this_year$value)
```

```{r sales plot, fig.width=6.5, fig.height=4, warning=FALSE, message=FALSE}
section1["sales_plot"]$sales_plot
```

`r paste(section1["sales_txt"]$sales_txt)`

###### Performance Target 2: Value of financing accessed by female FTF participants per \$1 of financing accessed by male FTF participants

```{r gender text,  fig.width=6.5, fig.height=.5, warning=FALSE, message=FALSE}
# finance
section1["gf_text"]$gf_text
```

```{r gender plot, fig.width=6.5, fig.height=4, warning=FALSE, message=FALSE}
section1["gender_finance_plot"]$gender_finance_plot
```

`r section1["gf_txt"]$gf_txt`

###### Performance Target 3: Number of cultivated hectares under climate adaptation/climate risk management practices and technologies with USG assistance

```{r hectares text, fig.width=6.5, fig.height=.5, warning=FALSE, message=FALSE}
section1["ht_text"]$ht_text
```

```{r hectares plot, fig.width=6.5, fig.height=4, warning=FALSE, message=FALSE}
section1["hectares_plot"]$hectares_plot
```

`r section1["ht_txt"]$ht_txt`

###### Performance Target 4: Value of private sector investment leveraged by the USG to support food security and nutrition

```{r PSI text, fig.width=6.5, fig.height=.5, warning=FALSE, message=FALSE}
section1["psi_text"]$psi_text
```

```{r PSI details, fig.width=7.5, fig.height=4.5, warning=FALSE, message=FALSE}
section1["psi_plot"]$psi_plot
```

`r section1["psi_txt"]$psi_txt`

###### Performance Target 5: Percent of women consuming a diet of minimum diversity (MDD-W)

```{r mddw details, fig.width=6.5, fig.height=.75, warning=FALSE, message=FALSE}
section1["mddw_text"]$mddw_text
```

```{r mddw plot, fig.width=6.5, fig.height=4, warning=FALSE, message=FALSE}
section1["mddw_plot"]$mddw_plot
```

`r section1["mddw_txt"]$mddw_txt`

### National Context

<!-- The following country context data has been collected from World Bank sources. -->

<!-- - FDI is foreign direct investment -->

<!-- -  -->

```{r context data, fig.width=6.5, fig.height=3.75, warning=FALSE, message=FALSE}
plot_df <- params$national_df %>%
    filter(ou == trimws(gsub("\\(.*$", "", gsub("USAID ", "",  ou_name )))) %>%
    mutate(year = as.Date(paste0("01-01-", year), format = "%m-%d-%Y")) %>%
    dplyr::select(ou, year, hunger, poverty, stunting, wasting) %>%
    unique() %>%
    pivot_longer(cols = c(3:6)) %>%
    mutate(name = case_when(name == "ag_value_add" ~ "Off Farm Production (in millions)",
                            name == "fdi" ~ "FDI",
                            name == "hunger" ~ "Food Insecurity (%)",
                            name == "poverty" ~ "Poverty (%)",
                            name == "stunting" ~ "Stunting (%)",
                            name == "wasting" ~ "Wasting (%)")) %>%
  mutate(txt = case_when(name == "Food Insecurity (%)" ~ "Prevalence of moderate or severe food insecurity in the population (%)"
                         , name == "Poverty (%)" ~ "Poverty headcount ratio at $2.15 a day (2017 PPP) (% of population)"
                         , name == "Wasting (%)" ~ "Prevalence of wasting, weight for height (% of children under 5)"
                         , name == "Stunting (%)" ~ "Prevalence of stunting, height for age (% of children under 5)")) %>% 
    filter(! name %in% c("FDI", "Off Farm Production (in millions)")) %>%
    drop_na() %>% ungroup()

natl_text <- if(nrow(plot_df) > 0L) {
  paste0("National level data was collected from the [World Bank’s Open Data portal](https://data.worldbank.org/) that measures key indicators at the national level.")
  } else knitr::asis_output(paste0("National context data is not available for "
         , trimws(gsub("\\(.*$", "", gsub("USAID ", "",  ou_name ))), "."))
```

`r paste0(natl_text)`

```{r context plot, fig.width=6.5, fig.height=3.75, warning=FALSE, message=FALSE}
if(nrow(plot_df) > 0L) {
  national_plot(plot_df
                , trimws(gsub("\\(.*$", "", gsub("USAID ", "",  ou_name ))))
} else NULL
  
```

## Agricultural Transformation Index Score

The IFPRI Agricultural Transformation Index (ATI) Score is a high level indicator of the status of agricultural market systems in each country.

```{r ati plot, fig.width=6.3, fig.height=3, warning=FALSE, message=FALSE}
p_ati <- ati_plot(params$ati, ou_name)
p_ati
```

## Budget Trend

At the Operating Unit level, the Performance Targets are based in part on the FY 2024 budget request. The budget chart below includes EG.3 money only.

```{r}
if(ou_name == "Bureau for Resilience and Food Security (RFS)") {
  knitr::asis_output("For the REFS Bureau, this value was divided by two to account for the large proportion of the budget that does not report on Performance Target indicators.")
}
```

```{r budget plot, fig.width=6.5, fig.height=4, warning=FALSE, message=FALSE}
# Budget --------
# ou_budget <- budget %>% filter(year %in% 2020:2024 & ou == trimws(gsub("\\(.*$", "", gsub("USAID ", "",  ou_name )))) %>%
#   mutate(budget = ifelse(ou == "Bureau for Resilience and Food Security (RFS)", budget/2, budget)
#          , type = ifelse(year > 2024, "653(a) Actual", "Requested")) 
# budget_hline <- ou_budget %>% filter(year == 2023) %>%
#   select(budget) %>% as.numeric()
# # # ----------- Prep data
# budget_plot <- ou_budget  %>%
#   rename(`Fiscal Year` = year, `EG3 Budget (000)` = budget) %>%
#   # ------------ ggplot
#   ggplot(aes(x = `Fiscal Year`, y = `EG3 Budget (000)`, linetype = type)) +
#   geom_point(size = 2.3) + geom_line(linewidth = 1, linetype = 4) +
#   geom_label_repel(aes(label = scales::dollar_format()(`EG3 Budget (000)`)), nudge_y = 100) +
# 
#   geom_hline(color = "#BA0C2F", yintercept = budget_hline, linewidth = 1, linetype = 2) +
#   # ------------ Set themes
#   # guides(color = guide_legend(position = "inside")) +
#   usaid_plot() + #common_theme() + 
#   theme(legend.position="bottom", plot.caption = element_text(size = 12) ) +
#   scale_y_continuous(labels = scales::label_dollar(), limits = c(0, NA)) +
#   ylab("") + xlab("") + 
#   # ggtitle(label = "EG3 Budget", subtitle = "Horizontal line is baseline") +
#   # labs(caption = "*REFS' targets were based on *half* of the FY 2023 budget request.")
#   labs(caption = paste0("* Values are in $1,000s\n**Red dashed line is the budget level used for target setting.", collapse="n"))
# budget_plot

if(params$ou_name == "Group Target") {
  # group_target_ous <- filter(params$pt_dat, is_group == TRUE ) %>% distinct(ro, ou)
  # make_budget_plot(budget = params$budget, ou_name = group_target_ous)
} else if(params$ou_name == "Group Target") {
    make_budget_plot(budget = params$budget, ou_name = params$ou_name)
} else if (params$ou_name == "FTF Initiative") {
  make_ftf_budget_plot(ftf_budget, ou_name = ou_name)
}
```

## Active Portfolio

The following activities are considered "active" based on their reporting in FY 2023 and expected FY 2024 reporting. The Analytics, Data and Learning Division defines an "active" activity as one that reported targets, actuals, or deviation narratives for the current year (FY 2023), or the next out year targets (i.e. FY 2024).

## Top Activities (Award Disbursements and Results)

This section highlights the `r min(n_activities, 5)` activities (out of the total `r n_activities` in the `r ou_name` portfolio) that have the highest level of FY 2023 annual disbursements and highest reported values for the relevant indicators.

```{r}
t5d <- params$top5_disbursements %>% 
  filter(ou_dis == ou_name) %>% 
  select(-starts_with("ou")) %>% 
  mutate(transaction_amt = scales::label_dollar()(transaction_amt)) %>% 
  select("Award Number" = award_number, a_code, a_name, "FY23 Disbursements" = transaction_amt
         , a_code, PT1 = "sales", PT2 = "gender_financing_ratio", PT3 = "hectares", PT4 = "three_yr_avg") %>% 
  make_human_readable_names() %>% 
  mutate( PT1 = ifelse(!is.na(PT1),  "X" , "-")
         , PT2 = ifelse(!is.na(PT2),  "X" , "-")
         , PT3 = ifelse(!is.na(PT3),  "X" , "-")
         , PT4  = ifelse(!is.na(PT4),  "X" , "-"))

if(nrow(t5d) > 1L) {
  knitr::asis_output(paste0("The first table below shows activities with the highest total transaction amounts. The columns to the right indicate if these activities are reporting on relevant PT indicators."))
} 

if(nrow(t5d) > 1L) {
  knitr::kable(t5d, table.attr = "style='width:8in;'")
} else knitr::asis_output(paste0("No activity records from DIS matched award numbers in the Phoenix database."))
  
```

The next table (below) shows the activities that reported the highest values for the relevant PT indicators. The total disbursements are included, if available.

```{r}
params$top5_results %>%
  mutate(across(c(sales, transaction_amt, psi), ~ scales::label_dollar()(.))
         , hectares = scales::label_number()(round(hectares, 0))) %>% 
  select(ou = ou_dis, "Award Number" = award_number, a_code, a_name
         , "Total Disbursements" = transaction_amt, `PT1: Sales` = sales
         , `PT3: Climate adaptive hectares` = hectares, `PT4: PSI` = psi) %>% 
  filter(ou == ou_name) %>% select(-ou) %>% 
  make_human_readable_names() %>% 
  knitr::kable(table.attr = "style='width:8in;'")
```

```{r}
knitr::include_graphics(params$mapfile)
```

### Appendix 1: Response to "Not on track" Performance Targets

This section provides space for Bangladesh to provide an explanation of why the following PTs are not on track and how you could adjust to be on track in the coming year(s). To help in your response(s), the relevant section of the FTF/GFS Key Issue Narrative (KIN) is provided, as it may be useful in drafting responses. Note that the KIN is addressing the sum of the out year targets (FY 2023) set by the Bangladesh activities that are reporting on each PT. The FY 2023 out year targets were set prior to the establishment of the FY 2030 Performance Targets, so the below explanations from the KIN may not apply to the Performance Target deviation.

-   In Section 4 of the FTF KIN, your OU discusses FY24 and FY25 targets, while these Scorecards are addressing progress against a trajectory from historical reporting to your OU’s FY30 target. Also, the FY 2023 out year targets were set prior to the establishment of the FY 2030 Performance Targets. Therefore, the below explanations from the KIN may not apply to these FY30 Performance Target deviations.

-   These responses will be used to compile a Congressional report, the GFSS Implementation Report, to discuss progress against the FTF FY 2030 Performance Targets, as mandated by the GAO.

-   Only PTs that are ‘Not on Track’ require review and explanation from the OU.

Include the following two components in each response:

1.  An explanation of why this target is not on track. Explanations may include that the OU/Mission was not aware of the target prior to planning activities. (Limit 100 words)

2.  Planned actions for ‘not on track’ targets. Planned actions may include the launch of new activities, building awareness, holding portfolio reviews, or other suggestions. (Limit 100 words)

```{r make OU KIN}
ou_kin <- kin %>% 
  filter(trimws(gsub("\\(.*$", "", ou_name )) ==  ou ) 
ou_kin <- if(nrow(ou_kin) > 0L) {
  ou_kin %>% bind_cols(section1["scores"]$scores)
} else tibble()
ou_label <-  trimws(gsub("USAID ", "", gsub("\\(.*$", "", ou_name )))
```

```{r, include = ou_kin[ou_kin$kin_section == "4a","score"] == "Not on track" }
knitr::asis_output("## Performance Target 1: Sales [Not on track]: \\n")
```

```{r, include = ou_kin[ou_kin$kin_section == "4a","score"] == "Not on track" }
knitr::asis_output(paste0("_Excerpt from FY23 KIN Section 4 to consider:_\\n"
                          , ou_kin$narrative_text[ou_kin$kin_section == "4a"], "\\n\\n"))
```

```{r, include = ou_kin[ou_kin$kin_section == "4a","score"] == "Not on track"}
knitr::asis_output(paste0("\\n#### Enter ", ou_label,"’s explanation of why this target is ‘Not on track’ below (Limit 100 words): \\n"))
```

```{r, include = ou_kin[ou_kin$kin_section == "4a","score"] == "Not on track"}
knitr::asis_output(paste0("\\n#### Enter ", ou_label,"’s planned actions for ‘Not on track’ targets below (Limit 100 words): \\n"))
```

```{r, include = ou_kin[ou_kin$kin_section == "4b","score"] == "Not on track" }
knitr::asis_output("## Performance Target 2: Gender financing ratio [Not on track]\\n")
```

```{r, include = ou_kin[ou_kin$kin_section == "4b","score"] == "Not on track" }
knitr::asis_output(paste0("_Excerpt from FY23 KIN Section 4 to consider: _\\n"
                          , ou_kin$narrative_text[ou_kin$kin_section == "4b"], "\\n\\n"))
```

```{r, include = ou_kin[ou_kin$kin_section == "4b","score"] == "Not on track" }
knitr::asis_output(paste0("\\n#### Enter ", ou_label,"’s explanation of why this target is ‘Not on track’ below (Limit 100 words): \\n"))
```

```{r, include = ou_kin[ou_kin$kin_section == "4b","score"] == "Not on track" }
knitr::asis_output(paste0("\\n#### Enter ", ou_label,"’s planned actions for ‘Not on track’ targets below (Limit 100 words): \\n"))
```

```{r, include = ou_kin[ou_kin$kin_section == "4c","score"] == "Not on track" }
knitr::asis_output("## Performance Target 3: Hectares under climate adaptive and risk management practices [Not on track]\\n")
```

```{r, include = ou_kin[ou_kin$kin_section == "4c","score"] == "Not on track" }
knitr::asis_output(paste0("_Excerpt from FY23 KIN Section 4 to consider: _\\n"
                          , ou_kin$narrative_text[ou_kin$kin_section == "4c"], "\\n\\n"))
```

```{r, include = ou_kin[ou_kin$kin_section == "4c","score"] == "Not on track" }
knitr::asis_output(paste0("#### Enter ", ou_label,"’s explanation of why this target is ‘Not on track’ below (Limit 100 words): \\n"))
```

```{r, include = ou_kin[ou_kin$kin_section == "4c","score"] == "Not on track" }
knitr::asis_output(paste0("#### Enter ", ou_label,"’s planned actions for ‘Not on track’ targets below (Limit 100 words): \\n"))
```

```{r, include = ou_kin[ou_kin$kin_section == "4d","score"] == "Not on track" }
knitr::asis_output("## Performance Target 4: Private sector investment [Not on track]\\n")
```

```{r, include = ou_kin[ou_kin$kin_section == "4d","score"] == "Not on track" }
knitr::asis_output(paste0("_Excerpt from FY23 KIN Section 4 to consider: _\\n"
                          , ou_kin$narrative_text[ou_kin$kin_section == "4c"], "\\n\\n"))
```

```{r, include = ou_kin[ou_kin$kin_section == "4d","score"] == "Not on track" }
knitr::asis_output(paste0("#### Enter ", ou_label,"’s explanation of why this target is ‘Not on track’ below (Limit 100 words): \\n"))
```

```{r, include = ou_kin[ou_kin$kin_section == "4d","score"] == "Not on track" }
knitr::asis_output(paste0("#### Enter ", ou_label,"’s planned actions for ‘Not on track’ targets below (Limit 100 words): \\n"))
```

```{r, include = ou_kin[ou_kin$kin_section == "4e","score"] == "Not on track" }
knitr::asis_output("## Performance Target 5: Minimumn Dietary Diversity for women (ZOI) [Not on track]\\n")
```

```{r, include = ou_kin[ou_kin$kin_section == "4e","score"] == "Not on track" }
knitr::asis_output(paste0("_Excerpt from FY23 KIN Section 4 to consider: _\\n"
                          , ou_kin$narrative_text[ou_kin$kin_section == "4c"], "\\n\\n"))
```

```{r, include = ou_kin[ou_kin$kin_section == "4e","score"] == "Not on track" }
knitr::asis_output(paste0("#### Enter ", ou_label,"’s explanation of why this target is ‘Not on track’ below (Limit 100 words): \\n"))
```

```{r, include = ou_kin[ou_kin$kin_section == "4e","score"] == "Not on track" }
knitr::asis_output(paste0("#### Enter ", ou_label,"’s planned actions for ‘Not on track’ targets below (Limit 100 words): \\n"))
```
